### 2025-01-29 analysis/preprocessing.qmd
fix(summaries): show  mean and median for all models
When correcting the best model_class_id, the previous commit grouped by best model type before summarizing the mean, max, and median. This commit updates valuesMean and valuesMedian columns to reflect all model classes  used in each study rather than only the best model class.

R_summary <- summarise(group_by(R_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))

### Now filter out best model
R_summary |> 
  ungroup() |> 
  filter(
    valuesMax == max(valuesMax), 
    .by = c(citekey, dimension)
  ) -> R_summary

@@

@@

```{r}
C_summary <- summarise(group_by(C_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
                        #feature_n_complexity_genre=first(feature_n_complexity_genre)
                        )
# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
C_summary[C_summary$citekey == "nguyen2017an",]$valuesMax <- C_summary[C_summary$citekey == "nguyen2017an",]$valuesMean

# 2025-01-24: averaging across quadrants for bhuvanakumar study
# subset study
bhuvanakumar <- subset(
  C_studies, 
  stringr::str_detect(
    C_studies$citekey,
    "bhuvanakumar"
    )
)
# group by algorithm to average across the four quadrants
bhuvanakumar$model_algorithm <- substr(
  bhuvanakumar$model_id, 
  1, 
  4
)
# take the average for each algorithm
bhuvanakumar |> 
  group_by(model_algorithm) |>
  mutate(values = mean(values)) -> bhuvanakumar
# overwrite values in C_summary
C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMean <- mean(unique(bhuvanakumar$values))
C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMedian <- median(unique(bhuvanakumar$values))
C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMax <- max(unique(bhuvanakumar$values))

C_summary |> 
  ungroup() |> 
  filter(
    valuesMax == max(valuesMax), 
    .by = c(citekey, dimension)
) -> C_summary

>>>>

# get best model class
R_studies |> 
  group_by(citekey, dimension, model_class_id) |> 
  summarize(best_model = max(values)) |> 
  filter(best_model == max(best_model)) -> best_model_class

best_model_class <- best_model_class[,c("citekey", "dimension", "model_class_id")]

R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))

R_summary <- left_join(R_summary, best_model_class)

@@

# These are encoded slightly differently, so need to use a different approach

# 2025-01-24: averaging across quadrants for bhuvanakumar study
# subset study
bhuvanakumar <- subset(
  C_studies, 
  stringr::str_detect(
    C_studies$citekey,
    "bhuvanakumar"
    )
)
# group by algorithm to average across the four quadrants
bhuvanakumar$model_algorithm <- substr(
  bhuvanakumar$model_id, 
  1, 
  4
)
# take the average for each algorithm
bhuvanakumar |> 
  group_by(model_algorithm) |>
  mutate(values = mean(values)) -> bhuvanakumar

C_studies <-C_studies |> filter(citekey != "bhuvanakumar2023em")
bhuvanakumar$model_algorithm <- NULL
C_studies <- rbind(C_studies, bhuvanakumar)

# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
C_studies[C_studies$citekey == "nguyen2017an",]$values <- mean(C_studies[C_studies$citekey == "nguyen2017an",]$values)

@@

```{r}
# get best model class
C_studies |> 
  group_by(citekey, dimension, model_class_id) |> 
  summarize(best_model = max(values)) |> 
  filter(best_model == max(best_model)) -> best_model_class_C

best_model_class_C <- best_model_class_C[,c("citekey", "dimension", "model_class_id")]

```{r}
C_summary <- summarise(group_by(C_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
                        #feature_n_complexity_genre=first(feature_n_complexity_genre)
                        )

C_summary <- left_join(C_summary, best_model_class_C)
